Indices Equations

### 2021-02-03 code/IndicesEquations.Rmd
Wrote out functions and descriptions for R package

To determine the migratoriness of a population, we calculate overlap of the population from two different times within the year, choosing those times to minimize the overlap, and reporting the overal.  The overlap is defined as:

>>>>

To determine the migratoriness of a population, we calculate overlap of the population from two different times within the year, choosing those times to minimize the overlap, and reporting the overall overlap.  The overlap is defined as:
